\documentclass[11pt]{article}
\usepackage{graphicx}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \huge \textbf{THANG LE}\\
    \hrulefill
\end{center}

\begin{center}
    Cau Giay, Ha Noi \textbullet \ lethang1281@gmail.com \textbullet \ 0981779204
    \textbullet \ lethang-apero.vercel.app
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of Engineering and Technology - VNU} \hfill Cau Giay, Ha Noi

Computer Science Bachelor | Data Analyst \hfill est. 06/2026
\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{ECOMUP} \hfill Hanoi

\textbf{Growth \& Business Development} \hfill 01/2026 -- Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Led market research and competitive analysis across product categories, identifying high-potential opportunities and validating demand before committing resources to new launches.
    \item Coordinated cross-functional teams (marketing, product, operations) to execute go-to-market strategies, aligning everyone on revenue targets and growth milestones.
    \item Built data dashboards tracking category performance (revenue, margins, conversion rates) to drive data-informed decisions on budget allocation and scaling priorities.
\end{itemize}
Key Skills: Market Research, Team Coordination, Go-to-Market, Data-driven Decision Making

\vspace{12pt}

\textbf{MISEN CO.LTD} \hfill Hanoi

\textbf{Performance Marketing Specialist} \hfill 01/2026 -- 03/2026
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Managed Google Ads Search campaigns with a \$1,500/day budget, maintaining target ROAS through continuous bid strategy optimization and keyword refinement.
    \item Set up and maintained conversion tracking via Google Tag Manager, ensuring accurate attribution and enabling data-driven budget allocation.
    \item Developed keyword strategies (match types, negative lists, search term mining) that reduced wasted spend and improved traffic quality.
\end{itemize}
Key Skills: Performance Marketing, Google Ads, Conversion Tracking, Budget Management

\vspace{12pt}

\textbf{Freelance E-commerce} \hfill Remote

\textbf{Shopify Store Operations \& CRO} \hfill 12/2025 -- 01/2026
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Built and operated Shopify storefronts end-to-end: product research, store setup, app integration, and conversion optimization in the supplements niche.
    \item Ran A/B tests on landing pages and offer structures, iterating on layouts to find better-converting combinations and reduce drop-off.
    \item Integrated upsell apps and Klaviyo email flows to recover abandoned carts and lift AOV --- combining marketing automation with product strategy.
\end{itemize}
Key Skills: Product Launch, A/B Testing, CRO, Marketing Automation

\vspace{12pt}

\textbf{Tai Chinh Xanh JSC.} \hfill Ha Noi

\textbf{E-commerce Operations \& Growth (Team Lead)} \hfill 09/2025 -- 12/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Led day-to-day operations for the ``Softie'' brand as a founding team member, keeping marketing, operations, and finance aligned on priorities and growth targets.
    \item Managed Facebook Ads campaigns (2--5M VND/day), briefing ad concepts, monitoring delivery, and iterating on underperforming creatives to improve ROAS.
    \item Analyzed campaign and sales data to find cost-reduction and revenue-growth opportunities, feeding findings directly into budget and strategy decisions.
\end{itemize}
Key Skills: Team Leadership, Startup Operations, Facebook Ads, Revenue Analysis

\vspace{12pt}

\textbf{NextStart Incubator - NextTech} \hfill Ha Noi

\textbf{Batch-1 Member - Growth \& Business Development} \hfill 06/2025 -- 10/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Selected into the inaugural cohort of NextTech's startup incubator. Conducted market research and competitive analysis for D2C product concepts, validating demand and identifying target segments.
    \item Led a cross-functional team (product, marketing, tech) to build and ship an MVP, developing go-to-market strategies and pitching growth plans to mentors and industry experts.
    \item Navigated ambiguity and resource constraints typical of early-stage ventures, making prioritization calls to keep the team focused on high-impact work.
\end{itemize}
Key Skills: Startup Building, Market Research, MVP Development, Team Leadership

\vspace{12pt}

\textbf{Thinkmay CO.,LTD} \hfill Ha Noi

\textbf{Growth Analyst} \hfill 06/2025 -- 09/2025
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked directly with the CEO to define growth priorities and align marketing initiatives with product positioning goals.
    \item Conducted user research and landing page analysis to identify UX friction points and improve conversion rates through A/B testing.
    \item Managed content production from concept to final asset, bridging the gap between marketing strategy and technical execution.
\end{itemize}
Key Skills: Growth Strategy, User Research, Marketing-Tech Integration

\newpage
\begin{center}
    \textbf{Skills \& Competencies}
\end{center}

\textbf{Startup \& Venture Building}

\textbf{MVP Development, Product-Market Fit, Go-to-Market, Resource Prioritization}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Hands-on experience building products from zero to one: market validation, MVP launch, and iterating toward product-market fit.
    \item Comfortable operating in ambiguity --- making prioritization calls with incomplete data, adapting strategies based on market feedback.
    \item Track record of shipping products in incubator and freelance settings, managing the full lifecycle from research to launch.
\end{itemize}

\vspace{8pt}

\textbf{Marketing \& Technology}

\textbf{Performance Marketing, Marketing Automation, Data Analytics, Web Development}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Deep hands-on experience with Google Ads, Facebook Ads, Meta Pixel, GTM, Klaviyo, and conversion tracking across platforms.
    \item Technical ability to build products (Next.js, React, TypeScript) and set up marketing infrastructure --- bridging marketing strategy and technical implementation.
    \item Use AI tools (Claude, Cursor) to accelerate data processing, report generation, and product development workflows.
\end{itemize}

\vspace{8pt}

\textbf{Team Leadership \& Cross-functional Coordination}

\textbf{Team Building, Stakeholder Management, Project Management}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Led small teams across multiple ventures, coordinating product, marketing, and operations functions toward shared business goals.
    \item Experience managing up (CEO/founder collaboration) and across (cross-functional alignment) in fast-moving startup environments.
    \item Certified in Scrum and Project Management, applying structured frameworks to maintain velocity in unstructured contexts.
\end{itemize}

\vspace{8pt}

\textbf{Market Research \& Business Analytics}

\textbf{Competitive Analysis, Audience Segmentation, Data-driven Strategy}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Conducted market research for product launches: trend analysis, competitor mapping, audience segmentation, and demand validation.
    \item Built dashboards and reports combining revenue, cost, and operational data to support strategic decisions.
    \item Translated data insights into actionable growth recommendations for stakeholders and leadership.
\end{itemize}

\vspace{12pt}


\begin{center}
    \textbf{Certificates}
\end{center}

\textbf{English Proficiency -} IELTS 7.0 (2022)

\textbf{Market Research \& Business Ideation -} NextTech \& Agile Academy (2025)

\textbf{Scrum Essence 2.0 -} Agile Academy (2025)

\textbf{Project Management -} Agile Academy (2025)

\vspace{12pt}
\begin{center}
    \textbf{Additional Information}
\end{center}
\textbf{Portfolio:} lethang-apero.vercel.app

\textbf{Github:} github.com/thnglee

\textbf{Linkedin:} linkedin.com/in/thang-lee-75365a258/


\end{document}
